Generating Interactive WebSocket Applications in TypeScript

### 2020-03-09 PLACES_2020/casestudy.tex
PLACES: proofread case study

Note that, by TypeScript's structural typing \cite{TypeScriptSpec}, replacing
\texttt{handleP2Move} on \cref{lineupdate} with a recursion of \texttt{handleP1Move} would be
type-correct -- this allows for better code reuse as opposed to defining
additional abstractions to work around the limitations of nominal typing in
\cite{Hybrid2016}.
There is also full type erasure when transpiling to JavaScript to run the
server code, so state space explosion is not a runtime consideration.

>>>>

Note that, by TypeScript's structural typing 
\cite{TypeScriptSpec}, replacing
\texttt{handleP2Move} on \cref{lineupdate} with a recursive 
occurrence of \texttt{handleP1Move} would be
type-correct -- this allows for better code reuse as opposed to 
defining
additional abstractions to work around the limitations of nominal 
typing in
\cite{Hybrid2016}.
There is also full type erasure when transpiling to JavaScript to 
run the server code, so state space explosion is not a 
runtime consideration.
